---
title: "Report on Field Trial \n FieldName"
output: word_document
---

```{r include=FALSE}
#--- working field-year ---#
library(here)
library(tmap)
library(sf)
library(ggplot2)
library(lwgeom)
library(measurements)
library(data.table)
library(tidyverse)
library(gdata)
library(mgcv)
library(daymetr)

field_year <- "Field_2019"

#--- field parameters ---#
source("https://raw.githubusercontent.com/brittanikedge/Precision-Agriculture-Producer-Materials/main/functions.R")
source("https://raw.githubusercontent.com/brittanikedge/DIFM/main/Functions.R")

#--- currently we do not have this as part of the field parameter data ---#
plot_width <- 60

```


```{r data-prep, cache=FALSE, include=FALSE}
# we need to bring all of the data into the document
analysis_data <- here("data.gpkg") %>% 
  st_read()

trial_design <- here("trial_new.gpkg") %>% 
  st_read()

as_applied_s <- st_read(here("asplanted_new.gpkg"))

yield <- st_read(here("yield_new.gpkg"))

yield_clean <- st_read(here("yield_clean.gpkg"))

boundary <- read_sf("boundary_new.gpkg")
weather <- download_daymet(site = "Field1", lat = cent_lat(boundary), lon = cent_long(boundary), start = 2000, end = 2018, internal = TRUE)

```

# Field Management Information
```{r include=FALSE}
tgts_ls <- unique(trial_design$SEEDRATE) 
tgts_ls <- tgts_ls[order(tgts_ls)]
s_sq <- 37000
planter_width <- 60
harvester_width <- 30
crop <- "corn"
rand <- "completely randomized"

```

# Trial Design and Implementation 

This was a seed and nitrogen trial on `r I(crop)` Below is the information about the trial rates of seed. Figure 1 presents the trial design. The trial design used `r I(length(tgts_ls))` seed rates. The treatments were laid out in a `r I(rand)` design.  The baseline treatment, what the producer would apply without participating in the trial, was (`r I(s_sq)` K).  Areas around the perimeter of the field received the baseline treatment and were not included in the analysis.  There were `r I(nrow(subset(trial_design, treat_type != 17)))` trial plots in total.  Each plot was `r I(plot_width)` feet wide. 

+ Baseline seed rate of `r s_sq` K.
+ Seed target rates: `r paste0(tgts_ls, "K", collapse = ",")` 
+ Planter width: `r planter_width` feet
+ Harvester width: `r harvester_width` feet

```{r trial-design, echo=FALSE}
map_poly(trial_design, "SEEDRATE", "Targeted Seed Rate")
```
The planting map highlights the quality of the seeding data. The planter implemented the trial with a high level of accuracy. 

```{r as-planted-seed-map, echo=FALSE}
#/*----------------------------------*/
#' ## As-planted Seed Rate
#/*----------------------------------*/
map_points(as_applied_s, "Rt_Apd_Ct_", "As-planted Seed Rate")
```
The raw yield map displays the importance of cleaning the data. We can see outliers throughout the field, where the harvester is registering very large yields. 
```{r echo=FALSE, fig.cap="Yield"}
#/*----------------------------------*/
#' ## Raw yield
#/*----------------------------------*/
map_points(yield, "Yld_Vol_Dr", "Yield (bu/ac)")

```

# Weather 

The figure below displays the monthly rainfall in inches across 2018. The color of each month compares the rainfall from 2018 with the 10-year average. We can see that 2018 was an average year with rainfall within 1 to 2 inches of the historic average.

```{r tgts-ap, echo=FALSE}
month_prec_graph(weather, comp_year = 2018)
```
